---
title: "Computational Musicology Portfolio"
author: "by TZ"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
source("compmus.R")
```

### Chroma Self-similarity Matrix 1

```{r}
"features/tymon-z-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  compmus_self_similarity(
    feature = pc,
    distance = "euclidean"                             # Change the distance
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()

```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

Interesting to see the relationship of the simple form on the visualisation! It's very much possible for me to see which bits in the score are where, especially on the timbre self-similarity matrix later on!

### Chroma Self-similarity Matrix 2

```{r}
"features/tymon-z-2.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  compmus_self_similarity(
    feature = pc,
    distance = "euclidean"                             # Change the distance
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic() 
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.



### Introduction

```{r}

```

*** 

This will be my portfolio


### Cepstrogram 1

```{r}
"features/tymon-z-1.json" |>                           # Change the track
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  ggplot(aes(x = time, y = mfcc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:12,
    minor_breaks = NULL,
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Coefficient Number", fill = NULL) +
  theme_classic()
  
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.

### Cepstrogram 2

```{r}
"features/tymon-z-2.json" |>                           # Change the track
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  ggplot(aes(x = time, y = mfcc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:12,
    minor_breaks = NULL,
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Coefficient Number", fill = NULL) +
  theme_classic()     
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.

### Chromogram of piece 1

```{r}
"features/tymon-z-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()           
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.

### Chromogram of piece 2

```{r}

"features/tymon-z-2.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()  
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.


### Timbre Self-similarity Matrix 1

```{r}
"features/tymon-z-1.json" |>                           # Change the track
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  compmus_self_similarity(
    feature = mfcc,
    distance = "euclidean"                             # Change the distance
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()  

```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.

### Timbre Self-similarity Matrix 2

```{r}
"features/tymon-z-2.json" |>                           # Change the track
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  compmus_self_similarity(
    feature = mfcc,
    distance = "euclidean"                             # Change the distance
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()  
```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'. 