---
title: "Computational Musicology Portfolio"
author: "by TZ"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```


### AI Song Contest Data

```{r}
library(tidyverse)
library(plotly)
aisc2024 <- read_csv("~/Downloads/aisc2024.csv")
g<-ggplot(aisc2024,                     # Set up the plot.
    aes(
      x = tempo,
      y = arousal,
      size = danceability,
      label=artist
    )
  ) +
  geom_point(alpha=0.9) +              # Scatter plot.
  #geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  #geom_text(                  # Add text labels from above.
   # x = 121,
   # y = 4.91,
   # label = "Onda Corta - Sud America",
   # size = 3,                 # Override size (not loudness here).
    #hjust = "left",           # Align left side of label with the point.
    #vjust = "center",         # Align vertical centre of label with the point.
    #angle = 30                # Rotate the text label
  #) +
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(60, 160),
    breaks = c(50, 100, 150, 200), # Specify grid lines
    minor_breaks = NULL       # Remove 'minor' grid lines.
  ) +
  #scale_y_continuous(         # Fine-tune the y axis in the same way.
    #limits = c(1, 9),
    #breaks = c(1, 5, 9),
    #minor_breaks = NULL
  #) +
  scale_fill_distiller() +  # Use the popular viridis colour palette.
  scale_size_continuous(      # Fine-tune the sizes of each point.
    #trans = "exp",            # Use an exp transformation to emphasise loud..
    #guide = "none"            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Tempo (BPM)",
    y = "Arousal (1-9)",
    size = "Danceability (0-1)"
  )
ggplotly(g)
```

*** 

Cool commentary about the music


### Introduction

```{r}

```

*** 

This will be my portfolio

### Description of submitted audio clips

```{r}

```

*** 

Both pieces are mine. The first one is called 'Conjunction no. 3' for violin, viola, cello and contrabass clarinet. 'Conjunctions' is a series where I explore simple rhythmical structures that change over time. 

The second file is an exercise for a class I have at Conservatorium called 'musical texture'. This one is an electronic piece, consisting of 4 voices on the same e-instrument of various pulsations. The 4 voices move through a harmony from my choral piece years ago and create a 'soundmass'.

### Analysis of the class corpus

```{r}

```

*** 

This will be my portfolio